### 2023-04-26 chapter2/chapter2.tex
Added paragraph summarizing Zarin 2019

>>>>

While these earlier studies were generally restricted to specific features or proteins, in 2019 Zarin \textit{et al.} demonstrated conservation of various features from a comprehensive set of IDR-associated properties in IDRs across the entire yeast proteome~\cite{Zarin2019}. By comparing the observed values of these features against those generated under a simulated model of evolution, they clustered IDRs by their ``evolutionary signatures,'' \textit{i.e.} patterns of conserved features. Furthermore, they identified specific biological functions associated with these groups, which for the first time provided a global view of the relationship between sequence and function in IDRs. A follow-up analysis expanded on this initial finding by applying techniques from machine learning and statistics to predict the functions of individual IDRs using their evolutionary signatures~\cite{Zarin2021}.
